### 2018-10-18 manuscript.rmd
nave partitioned alignment s4 object
calculates clade rectangles and plots them, native ggplot extension not working

taxa = 
	read_tsv("taxonomy_info/taxon_table.tsv") %>% 
	distinct( relabelled_name, clade_assignment, ncbi_tax_id ) %>%
	dplyr::rename( taxon=relabelled_name, clade=clade_assignment )

@@

>>>>

taxa = 
	read_tsv("taxonomy_info/taxon_table.tsv") %>% 
	distinct( relabelled_name, clade_assignment, ncbi_tax_id ) %>%
	dplyr::rename( taxon=relabelled_name, clade=clade_assignment ) %>%
	mutate( clade = factor( clade, levels=clades )  )

@@

a_file = "~/Desktop/animal_root/blast/phylips/Chang2015_Chang2015.phy"
p_file = "~/Desktop/animal_root/blast/phylips/Chang2015_Chang2015.nex"
msa = PartitionedMultipleAlignment( a_file, p_file, taxa )

D=clade_rects(msa)

ggplot() + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect(data=D, mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	scale_fill_discrete(guide = guide_legend(reverse=TRUE))
```
